---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MyPackage

<!-- badges: start -->
[![R-CMD-check](https://github.com/sangovae/MyPackage/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/sangovae/MyPackage/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

The goal of MyPackage is to visualize the invasion of the invasive Asian hornet (<em>Vespa velutina</em>) in Flanders.

MyPackage can produces maps or bar charts per year of known observations of Asian hornets (Vespa velutina) in Flanders.

The user defines the year range. Occurrences are retrieved from the Global Biodiversity Information Facility (GBIF).


## Example

```{r example}
library(MyPackage)
data2017_2019 <- vespa_data(2017,2019)
data2017_2019
```

```{r bar chart, echo = FALSE}
vespa_chart(data2017_2019)
```

```{r map, echo = FALSE}
vespa_map(data2017_2019)
```

