---
title: "Overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MyPackage)
```

This vignette gives an overview of the package `MyPackage`.

The goal of this package is to produce a map or bar chart per year of known observations of Asian hornets *Vespa velutina* in Flanders, and you are able to filter this information on a year range.

## 1. Functions 

Three different functions are available.

### 1.1 `vespa_data`

`vespa_data` retrieves occurrences of *Vespa velutina* in Flanders from the the Global Biodiversity Information Facility (GBIF) for a given year range. It is also possible to retrieve the data for a single year. In case of a year range: the first parameter is the lower year, the second parameter is the higher year, e.g. 2017, 2019 (and NOT 2019, 2017). *Vespa velutina* was first observed in 2017 in Flanders. Therefore, your year range should start at least at 2017. 
Keep in mind that retrieving data from GBIF takes time, especially when there are many occurrences.

```{r}
vespa_data(2019,2021)
```

### 1.2 `vespa_chart`

`vespa_chart` creates a bar chart of observations per year. `vespa_chart` requires the parameter `data`, which is a `tibble` created by using the function `vespa_data`.

### 1.3 `vespa_map`

`vespa_map` creates a map of observationsin Flanders during a given year range. `vespa_map` requires the parameter `data`, which is a `tibble` created by using the function `vespa_data`. 


## 2. Datasets

In this package, two data files are available:

### 2.1 `mapFlanders`

`mapFlanders` is map of Flanders retrieved from Google. `vespa_map` uses it as background for the geographical visualization of the invasion of Asian hornets in Flanders.

### 2.1 `vespadata_2019_2021`

This package also includes 
Create R code that allows:
1. To define a year range (e.g. 2019-2021).
2. To retrieve occurrences from the Global Biodiversity Information Facility (GBIF) for that
year range of Vespa velutina in Flanders.
3. To present the result as a map of observations.
4. To present the result as a bar chart of observations per year.
Your code should be documented and tested. Your code should be maintained on GitHub.


